Biogeography of crop progenitors and wild plant resources during the transition to agriculture in West Asia

### 2024-12-23 analysis/analysis.qmd
Add topographic predictors

@@

@@

dem <- read_stars(derived_data("dem", "srtm_15plus_w_asia.tif"))
names(dem) <- "elevation"

# TODO: slope
# TODO: aspect
# TODO: twi
```

```{r data-environment}
# TODO: resample to common res
# TODO: reproject
# TODO: combine
# TODO: fill NAs?
```

>>>>

```{r setup-whitebox}
```

@@

# TODO: derived terrain products are two big to commit
# TODO: does TWI actually make sense at this resolution? Could start with (much)
# higher res, then upscale?
terrain <- read_stars(derived_data("dem", c("srtm_15plus_w_asia.tif", 
                                            "srtm_15plus_w_asia_slope.tif",
                                            "srtm_15plus_w_asia_aspect.tif",
                                            "srtm_15plus_w_asia_wetness.tif")))
names(terrain) <- c("elevation", "slope", "aspect", "wetness")
```

```{r data-environment}
# For time-invariant predictors, collapse attributes into dimension and 
# duplicate to create a dummy period dimension
# TODO: maybe need to downsample first?
terrain <- st_redimension(terrain, name = "variable")
terrain <- do.call(c, rep(list(terrain), length(climate_periods)))
names(terrain) <- names(climate_periods)
terrain <- st_redimension(terrain, name = "period") # TODO: why *so* slow?

soil <- st_redimension(soil, name = "variable")
soil <- do.call(c, rep(list(soil), length(climate_periods)))
names(soil) <- names(climate_periods)
soil <- st_redimension(soil, name = "period")

# Resample to common grid
terrain <- st_warp(terrain, climate, use_gdal = TRUE, method = "cubicspline")
soil <- st_warp(soil, climate, use_gdal = TRUE, method = "cubicspline")

# TODO: combine and split variable
# TODO: fill NAs?
```

@@
